% Operating a Human-Governed Multi-Machine LLM Agent Fleet: An Experience Report
% Preprint v0.1, published 2026-07-17 in this repository.
% Target: arXiv cs.MA (cross-list: cs.DC, cs.SE); submission pending endorsement.
% Author: Anton Dziatkovskii, ORCID 0000-0001-7408-3054
% Honesty note: every number in the Measured Results section comes from a live run
%   of demo/demo.py on one of the fleet's laptops, 2026-07-16; the machine-readable
%   output is demo-run-hp17-20260716.json in this directory. Nothing is simulated.
%   Ablation evidence = historical production incidents (docs/FAILURE-MODES.md).
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{orcidlink}
\usepackage{booktabs}

\title{Operating a Human-Governed Multi-Machine LLM Agent Fleet:\\ An Experience Report}
\author{Anton Dziatkovskii\,\orcidlink{0000-0001-7408-3054}\\
\small Platinum Software Development Company, Brisbane, Australia\\
\small \texttt{dzyatkovskiy.a2@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
Most published multi-agent LLM systems are single-process orchestrations evaluated on benchmarks. We report on something different: a fleet of LLM agents distributed across five physical machines (an always-on hub, laptops, a family computer, and a VPS anchor), operated continuously for roughly two months (June--July 2026) on real knowledge work by a non-technical founder and his collaborators. The fleet negotiates decisions through a deterministic consensus protocol (\emph{propose $\to$ counter $\to$ accept $\to$ commit} over an append-only, single-writer-per-machine event log), communicates over a dual-rail bus (synced file mailbox plus a group chat that humans also read), enforces an acknowledgement discipline in which silence past an SLA is an incident, and gates every risky action behind a deterministic risk-tier tripwire that escalates to a dedicated human channel. The safety-critical layer makes zero LLM calls: it is auditable file I/O, and we show it derives full fleet state at microsecond cost. This is an experience report, not a benchmark study. Its evidence is (i) a reproducible offline harness --- five self-checking scenarios covering the happy path, the human gate, the tripwire, split-brain, and ledger corruption, all passing on commodity hardware --- and (ii) a catalog of nine production failure modes, each of which occurred before its guard existed, giving an unusual, historically grounded form of ablation: for every guard we can state what the system actually did without it. We distill the design principles that survived contact with production (single-writer files, dual-rail by construction, delivery is not completion, detect what you cannot prevent, a human gate needs an exit, alert-channel purity, owner-repairability) and state our limitations plainly: this is an $N{=}1$ longitudinal case study with no comparative baseline. Reference implementation: \texttt{claude-consensus} (MIT).
\end{abstract}

\section{Introduction}
Run an LLM agent on more than one computer and a new class of problems appears that no amount of model quality fixes. Machines drift apart: a fix lands on one host and the others never hear of it. The human becomes the courier, copy-pasting between terminals, and thereby the single point of failure. ``Sent'' silently becomes ``done'': an agent hands off a task, nobody confirms it landed, and silence is misread as success. And the synchronization link itself dies quietly, muting half the fleet for hours before anyone notices.

The multi-agent LLM literature largely does not address this regime. Frameworks such as AutoGen \cite{autogen}, CrewAI, MetaGPT \cite{metagpt}, and LangGraph orchestrate multiple \emph{roles} inside one process or one service; the distribution of agents across physically separate, independently failing machines --- each with its own uptime, its own operator, and its own copy of shared state --- is left to the reader. Classical distributed consensus (Paxos \cite{paxos}, Raft \cite{raft}, PBFT \cite{pbft}) solves a different problem in kind: agreement on an ordered log among identical deterministic replicas, whereas our agents are heterogeneous, non-deterministic proposers negotiating \emph{semantic} decisions (``adopt this rule,'' ``migrate this routine to the hub'') where the safety property that matters is not consistency but \emph{no unsanctioned irreversible action}.

This paper reports what it took to run such a fleet in production: five machines, two months of continuous operation (June--July 2026), real work (knowledge-base curation, content pipelines, CRM operations, system administration), a non-technical owner, and a hard requirement that the human is woken up for exactly two reasons --- a risky (Tier-2) action or a true deadlock --- and nothing else.

Our contributions are those of an experience report:
\begin{enumerate}
\item A working architecture for human-governed multi-machine agent coordination: a deterministic consensus core with a risk-tier human gate, a dual-rail message bus with acknowledgement discipline, single-writer append-only state, and layered self-healing for the sync fabric (\S\ref{sec:system}).
\item A reproducible, offline, zero-token evaluation harness --- five self-checking scenarios that double as the engine's integration test --- with measured results on commodity hardware (\S\ref{sec:eval}).
\item A catalog of nine production failure modes with root causes and the guards they produced (\S\ref{sec:failures}). Because every guard was added \emph{after} its incident, the catalog constitutes a historically grounded ablation: for each safety mechanism we can document the behavior of the system without it.
\item Distilled design principles and honest limitations (\S\ref{sec:principles}, \S\ref{sec:limits}).
\end{enumerate}

The theoretical frame behind the protective design --- three antagonistically coupled control circuits from the Gorsky--Anokhin homeostatic lineage --- is developed in a companion preprint \cite{homeostatic}; a second companion applies the same negative-feedback lens to token economies \cite{lechatelier}. This paper is deliberately the practitioner's side of that pair: what we built, what broke, and what we measured.

\section{Related work}\label{sec:related}
\paragraph{Multi-agent LLM frameworks.} AutoGen \cite{autogen} popularized conversational multi-agent orchestration; MetaGPT \cite{metagpt} and ChatDev \cite{chatdev} structure role-played software teams; LangGraph adds graph-structured control flow with human-in-the-loop interrupts; AgentScope \cite{agentscope} supports actor-based distributed deployment. To our knowledge, none packages the combination we found necessary in production: physically distributed consensus with bounded rounds and a leader tie-break, a \emph{deterministic} risk-tier tripwire that force-escalates mislabeled dangerous actions to a dedicated human channel, an acknowledgement/liveness SLA between hosts, and self-healing of the underlying sync fabric. Our claim is emphatically \emph{not} algorithmic novelty; it is that this systems-level integration is what actually keeps a real fleet coherent, and that it is simple enough to run on the standard library alone.

\paragraph{Classical consensus.} Paxos \cite{paxos}, Raft \cite{raft}, and PBFT \cite{pbft} provide state-machine replication among identical replicas. We borrow their vocabulary (leader, log, split-brain) but solve a smaller and different problem: a handful of trusted-but-fallible machines negotiating semantic proposals at human timescales (minutes to hours, SLA-timed ticks), with the human as the ultimate authority for a defined risk class. Where classical consensus prevents divergence, we often only \emph{detect} it and refuse to let it pass as success (\S\ref{sec:failures}D) --- a deliberate trade for auditability and owner-repairability.

\paragraph{Agent memory.} Long-term memory systems for LLM agents range from tiered self-editing memory (MemGPT \cite{memgpt}) to automatically extracted knowledge graphs with hybrid retrieval (GraphRAG \cite{graphrag}, HippoRAG \cite{hipporag}, Zep/Graphiti \cite{zep}, A-MEM \cite{amem}). The fleet's shared memory substrate (\S\ref{sec:memory}) differs in two pragmatic respects: the knowledge graph is \emph{human-curated} (wikilink structure maintained in the owner's Obsidian vault) rather than model-extracted, and a small always-loaded \emph{fact ledger} rides in every session's context at zero retrieval cost, with vector search plus cross-encoder reranking reserved for the long tail. We make no novelty claim for the ingredients; the report is on how this combination behaves under months of real use.

\paragraph{Human oversight of agents.} Human-in-the-loop gating for agent tool use is common practice (framework interrupts, permission systems, guardrail toolkits). Our variant is narrow but strict: the gate is \emph{deterministic} (keyword-tier tripwire, not model judgment), it fails \emph{closed} (a mislabeled dangerous action is force-escalated), the approval has a first-class recorded exit path (\S\ref{sec:failures}F), and the alert channel is kept free of routine traffic by construction (\S\ref{sec:failures}H).

\section{The fleet and its coordination layer}\label{sec:system}
\subsection{Setting}
The fleet comprises five machines: an always-on desktop hub (also the GPU worker), two laptops, a family member's computer, and a small always-on VPS that acts as an anchor/coordinator. Each machine runs an interactive LLM agent (Claude Code) plus scheduled headless routines. State that must be shared --- the knowledge vault, configuration, the message bus --- replicates over Syncthing; nothing depends on a central server. The operators are a non-technical founder and two collaborators; ``the human'' below refers to the founder unless noted.

\subsection{Dual-rail bus}
Every machine-to-machine message is sent on two rails at once, by construction: (1) a file mailbox inside the synced folder, and (2) a group chat that both machines and humans read. A single entry point (\texttt{bus\_send.py}) makes single-rail sends impossible. The design intent is that a dead rail becomes a \emph{signal} (the rails disagree) rather than a silent downgrade. Messages carry IDs; every direct order expects an explicit acknowledgement, then a result report. Silence past the SLA (tens of minutes) triggers an automated chase, then escalation --- ``delivered'' is never allowed to masquerade as ``done.''

\subsection{Single-writer, append-only state}
Every writer appends only to its own file (per-machine shards, JSONL). Two machines never write the same file, so whole-file synchronization never conflicts; merge is a read-time operation. This one invariant eliminated the entire class of sync-conflict bugs from the coordination layer, at the cost of a merge-on-read that we show is microsecond-cheap (\S\ref{sec:eval}).

\subsection{The consensus protocol}
Decisions flow through \emph{propose $\to$ counter $\to$ accept $\to$ commit} over the append-only ledger, with a bounded round count, per-step timeouts, a fixed leader for tie-breaks (bounded ``disagree-and-commit''), capability-based addressing (a task routes to whichever node can serve it), and split-brain detection on merge. Proposals carry a risk tier. Tier-0/1 (reversible, internal) actions commit autonomously on agreement or leader tie-break; Tier-2 (money, irreversible, outward-facing, secrets) \emph{cannot} auto-commit: a deterministic tripwire bumps any proposal whose subject contains a dangerous verb (\texttt{delete}, \texttt{send}, \texttt{transfer}, \texttt{publish}, \dots) to Tier-2 regardless of the label the proposing agent chose, and commit is refused until a human approval is recorded as a first-class ledger event. ``Globally done'' additionally requires two distinct verifiers, at least one independent of the committer, with a rubber-stamp guard rejecting verbatim-duplicated proofs.

The safety-critical layer --- tie-break, the Tier-2 gate, the tripwire, split-brain detection, verification counting --- is deterministic standard-library Python with zero LLM calls. The LLM does only what only an LLM can (propose content, judge a counter), \emph{above} the engine. This split is the central safety decision of the design: everything that guards against catastrophe is code you can audit line by line, not model output you have to trust.

\subsection{Governance: leader/follower canon and rules-as-files}
Shared behavioral rules (the fleet's ``constitution'' and operating rules) live as versioned markdown files loaded into every agent's context. Exactly one machine (the hub) commits changes to this canon; followers receive it read-only and propose amendments through the bus. Local work on any machine stays fully autonomous. This asymmetry ended write-write wars over the rulebook while preserving peer initiative --- the same leader-for-canon, peers-for-work split that the consensus layer uses for tie-breaks.

\subsection{Self-healing sync}
The sync fabric gets three layers of self-heal: a watchdog that alerts on \emph{state change} rather than on every run (alert-fatigue is a safety problem, \S\ref{sec:failures}H); a bounded auto-nudge that asks the dead peer's own scheduled robot to restart its daemon; and an auto-failover that mirrors file-rail messages to the chat rail while a peer is dark. Liveness is judged from live connection state and fresh heartbeats, never from stale file markers.

\subsection{The shared memory substrate}\label{sec:memory}
The fleet's long-term memory is the owner's knowledge vault: thousands of markdown notes with human-curated wikilinks, replicated to all machines. Retrieval is layered by cost: (1) a small always-loaded fact ledger (an index of one-line facts, each backed by a file) rides in every session at zero retrieval cost; (2) deterministic tools (SQL over indexed stores, name search, grep) answer what they can for zero tokens; (3) vector search over the curated corpus with cross-encoder reranking retrieves the semantic long tail; (4) the wikilink graph supplies relationship context that embedding similarity misses. The division of labor mirrors the consensus engine's: deterministic layers do everything they can; the model spends tokens only on judgment and synthesis. We report this substrate as part of the fleet because in practice coordination and memory failures interact --- a peer acting on a stale fact is indistinguishable, from the outside, from a peer that never got the message.

\section{Evaluation method}\label{sec:eval-method}
An honest evaluation of a production fleet run by its own authors faces obvious epistemic hazards, so we constrain ourselves to two forms of evidence, both checkable by a skeptical reader.

\paragraph{(1) A reproducible offline harness.} \texttt{demo/demo.py} in the published repository runs the \emph{published} reference engine through five scenarios on one host, simulating two machines by switching the machine identity between calls, with the chat rail disabled --- no network, no packages, no API key, no LLM. Each scenario self-checks its end-state; the process exits 0 only if all pass, so the demo doubles as the integration test. Scenario A exercises the happy path through double verification; B proves a Tier-2 action cannot auto-commit and that a recorded approval unblocks it; C proves the tripwire force-escalates a dangerous action mislabeled Tier-0; D manufactures a split-brain (both partitions commit) and proves it is caught and escalated on heal, never reported as success; E injects a corrupt line into a shard and proves events after it still parse.

\paragraph{(2) The failure catalog as historical ablation.} Conventional ablation removes a component and measures degradation. We did not have to simulate this: for each of the nine guards in \S\ref{sec:failures}, production \emph{ran without the guard first}, and the incident that resulted is documented (symptom, root cause, fix, code link) in the repository's failure-mode catalog. This is weaker than controlled ablation --- one incident per guard, no counterfactual frequency --- and stronger in one respect: the ``ablated'' condition ran in the real environment, not a sandbox. We present it as what it is.

What we explicitly do \emph{not} claim: comparative performance against other frameworks (none targets this regime, and we have no baseline), statistical significance (this is an $N{=}1$ longitudinal case), or any measured-adoption evidence beyond our own operation.

\section{Measured results}\label{sec:eval}
All numbers in this section are from a single run of the public harness on one of the fleet's laptops (Windows 11, consumer hardware, Python 3.x, cold-ish disk cache), 2026-07-16; the machine-readable output is committed alongside the draft. Absolute milliseconds vary by machine --- the claim is the shape, not the digit.

\begin{table}[h]
\centering
\small
\begin{tabular}{llrrl}
\toprule
 & Scenario & Wall time & CLI calls & Self-checked end-state \\
\midrule
A & Happy path & 999.8 ms & 6 & committed; 2 verifiers incl.\ 1 independent \\
B & Human gate & 769.0 ms & 5 & auto-escalated; commit refused until approval \\
C & Tier tripwire & 309.0 ms & 2 & mislabeled Tier-0 stored as Tier-2, escalated \\
D & Split-brain & 782.0 ms & 5 & dual commit detected as conflict, escalated \\
E & Corrupt line & 656.5 ms & 4 & events after corrupt line still read \\
\midrule
 & \multicolumn{4}{l}{LLM calls across all scenarios: \textbf{0} \qquad tokens: \textbf{0} \qquad result: \textbf{5/5 pass}} \\
\bottomrule
\end{tabular}
\caption{Harness run, 2026-07-16, fleet laptop. Each step is a fresh Python process; wall time is dominated by interpreter startup, not consensus logic.}
\label{tab:scenarios}
\end{table}

Because each CLI verb pays full process startup, the harness also derives state in-process over a realistic ledger: merging all shards and recomputing the state of \textbf{50 proposals / 250 events took 1{,}717.8\,\textmu s per full pass} on this machine --- about 6.9\,\textmu s per event, with no incremental cache to invalidate and no index to corrupt, because the engine re-reads the append-only log and re-derives everything each time. In production the verbs run as scheduled ticks every 10--20 minutes, so even the $\sim$100\,ms process startup is irrelevant. The coordination layer is, for practical purposes, computationally free; the binding constraints are the sync rail (seconds to minutes) and the per-peer SLA timeouts (default 30 minutes) --- which is exactly where the engineering effort went.

\section{Nine production failure modes}\label{sec:failures}
Each entry below occurred in production before its guard existed. We compress to symptom $\to$ root cause $\to$ guard $\to$ lesson; the public catalog carries code links for each.

\paragraph{A. The leader's infinite self-accept loop.} Overnight the leader wrote 17 identical ACCEPT events on its own proposal, one per tick, never converging: an accept only advances state when cast by a non-proposing machine, so the leader's self-accept was a no-op reissued forever. \emph{Guard:} on timeout of the leader's own Tier-0 proposal the tie-break is a direct COMMIT, and a self-accept that cannot advance state is never re-cast. \emph{Lesson:} a retry that provably cannot change state is an infinite loop with extra steps; make the terminal action terminal.

\paragraph{B. Tier mis-classification, and the tripwire's own false positive.} The human gate is only as good as the tier label, so a deterministic keyword tripwire force-bumps dangerous verbs regardless of the label. Its first version matched substrings, so the filename \texttt{bus\_send.py} tripped ``send'' and force-escalated harmless proposals. \emph{Guard:} word-boundary matching (suffix inflections still match; phrase terms keep substring semantics), removing a false class while keeping every true term. \emph{Lesson:} a safety gate that cries wolf gets disabled by the humans it annoys; precision is a safety property.

\paragraph{C. A corrupt shard line eating everything after it.} One malformed line (partial write, sync-conflict junk) silently dropped every subsequent event in that shard; state went stale with no error. \emph{Guard:} parse per line, not per file; a bad line is skipped, its neighbors are read. \emph{Lesson:} in an append-only log fed by unreliable writers, corruption is local --- make the reader treat it that way.

\paragraph{D. Split-brain: both partitions commit.} During a partition each side saw ``agreed,'' believed it owned the apply, and committed; healing produced two conflicting COMMITs. \emph{Guard:} two COMMITs from distinct actors on one proposal are detected on merge, marked \texttt{conflict} --- never silently ``committed'' --- and escalated for human reconciliation with the leader's log authoritative. \emph{Honest limitation:} this \emph{detects} rather than \emph{prevents}; prevention would need a distributed lock we deliberately did not build, because the owner must be able to reason about the system. \emph{Lesson:} if you cannot cheaply prevent a fault, at minimum refuse to let it masquerade as success.

\paragraph{E. ``Done'' nobody independently checked.} The machine that applied a change also verified it, and the fleet accepted the single self-report. \emph{Guard:} globally-done requires $\geq 2$ distinct verifiers, at least one not the committer, plus a rubber-stamp guard rejecting verbatim-duplicated proofs. \emph{Lesson:} verification by the party that did the work is a status update, not a check.

\paragraph{F. Tier-2 proposals stuck escalated forever.} A correctly escalated action got its human ``yes'' in chat --- and nothing could carry that yes into the ledger, so the proposal sat escalated permanently. \emph{Guard:} an \texttt{approve} verb records the human decision as a first-class event with a required who/where/message-id proof; commit then admits Tier-2 only with a recorded approval. \emph{Lesson:} a human gate needs an exit, not just an entrance; a safety stop with no resume path is a different outage.

\paragraph{G. Same-second events sorted by filename.} Two events in the same second sometimes sorted by shard filename rather than causality, deriving a wrong state. \emph{Guard:} microsecond timestamps. \emph{Lesson:} if the ordering key is coarser than the event rate, you are sorting by luck.

\paragraph{H. The deadlock alert drowning in heartbeats.} The ``a human is needed now'' ping shared a channel with routine heartbeats, and the humans missed it. \emph{Guard:} a dedicated human-alert channel reserved for exactly two message types --- a Tier-2 approval request and a true deadlock; routine traffic is banned by construction. \emph{Lesson:} an alert channel that also carries noise is not an alert channel.

\paragraph{I. Regressive votes from a restored backup.} A machine restored from an older backup re-cast votes it had already superseded, re-opening settled proposals. \emph{Guard (production):} a per-machine vote watermark in the synced decisions directory --- a new vote must be strictly newer than that machine's last recorded vote on the proposal; peers re-sync the newer watermark, so restoring one machine cannot roll it back. This guard is documented but intentionally not in the minimal published reference, and we flag that asymmetry explicitly. \emph{Lesson:} the protocol and the fleet operations around it fail differently; publishing honestly means saying which guards belong to which.

\section{Design principles that survived production}\label{sec:principles}
\begin{enumerate}
\item \textbf{Single-writer everything.} One file, one writer; merge on read. This is the cheapest consistency mechanism we know of that a non-specialist can audit.
\item \textbf{Dual-rail by construction, not by policy.} If sending on one rail is possible, it will happen; make the single entry point do both, and treat rail disagreement as signal.
\item \textbf{Delivery is not completion.} Every order expects an ACK and then a result; silence past SLA is an incident. The sender owns the outcome.
\item \textbf{Determinism guards; models propose.} Every safety-critical decision (tiers, gates, tie-breaks, split-brain, verification counting) is auditable code with zero LLM calls. Token spend is reserved for judgment.
\item \textbf{Detect what you cannot afford to prevent} --- and never let the detected fault report success (split-brain, D).
\item \textbf{A human gate needs an exit} (F) \textbf{and a pure channel} (H). Both halves failed in production before we learned this.
\item \textbf{Fail-closed tripwires with word-boundary precision} (B): the gate must fire on mislabeled danger and must not fire on filenames, or humans will disable it.
\item \textbf{Owner-repairability as a design bound.} Standard library only, no server, no database, no distributed lock: every component must be repairable by a non-technical owner ``with a hammer and a screwdriver.'' Several stronger designs were rejected on this bound alone.
\end{enumerate}

\section{Limitations}\label{sec:limits}
This is an $N{=}1$ case study of one fleet, operated by its authors, over roughly two months; nothing here is a controlled experiment. The harness measures the engine on one host --- there is no transport latency in Table~\ref{tab:scenarios}; real cross-machine convergence is dominated by the sync rail and SLA timers (seconds to tens of minutes). The failure catalog is evidence of guards earned, not proof of future safety; the published reference is a sanitized subset of the production engine, and we mark production-only guards explicitly. We report no comparative baseline because we know of no framework targeting the same regime, which is itself a claim readers should treat skeptically. Finally, the memory substrate's contribution is described qualitatively; instrumenting recall quality under fleet conditions is future work, and we would rather say so than invent a number.

\section{Conclusion}
A fleet of LLM agents across physically separate machines can run real work for months under a discipline simple enough for its non-technical owner to repair: deterministic consensus over single-writer logs, dual-rail messaging with acknowledgement debt, a fail-closed human gate for irreversible actions, and layered self-healing for the fabric underneath. None of the individual mechanisms is novel; the report is that this particular integration holds up, what it cost to learn, and exactly where it still fails. The reference implementation, harness, and failure catalog are public (\texttt{claude-consensus}, MIT); the theoretical frame is developed in companion work \cite{homeostatic,lechatelier}. We offer the scars as prior art so others do not pay for them twice.

\begin{thebibliography}{99}
\bibitem{autogen} Q. Wu et al. AutoGen: Enabling next-gen LLM applications via multi-agent conversation. arXiv:2308.08155, 2023.
\bibitem{metagpt} S. Hong et al. MetaGPT: Meta programming for multi-agent collaborative framework. arXiv:2308.00352, 2023.
\bibitem{chatdev} C. Qian et al. ChatDev: Communicative agents for software development. ACL, 2024.
\bibitem{agentscope} D. Gao et al. AgentScope: A flexible yet robust multi-agent platform. arXiv:2402.14034, 2024.
\bibitem{paxos} L. Lamport. The part-time parliament. ACM TOCS 16(2), 1998.
\bibitem{raft} D. Ongaro, J. Ousterhout. In search of an understandable consensus algorithm. USENIX ATC, 2014.
\bibitem{pbft} M. Castro, B. Liskov. Practical Byzantine fault tolerance. OSDI, 1999.
\bibitem{memgpt} C. Packer et al. MemGPT: Towards LLMs as operating systems. arXiv:2310.08560, 2023.
\bibitem{graphrag} D. Edge et al. From local to global: A graph RAG approach to query-focused summarization. arXiv:2404.16130, 2024.
\bibitem{hipporag} B. Jimenez Gutierrez et al. HippoRAG: Neurobiologically inspired long-term memory for LLMs. NeurIPS, 2024.
\bibitem{zep} P. Rasmussen et al. Zep: A temporal knowledge graph architecture for agent memory. arXiv:2501.13956, 2025.
\bibitem{amem} W. Xu et al. A-MEM: Agentic memory for LLM agents. arXiv:2502.12110, 2025.
\bibitem{homeostatic} A. Dziatkovskii. Homeostatic governance: A Gorsky--Anokhin alternative to the Viable System Model for decentralized organizations. Preprint, 2026.
\bibitem{lechatelier} A. Dziatkovskii. Le Chatelier tokenomics: A thermodynamic--homeostatic framing of negative-feedback token supply control. Preprint, 2026.
\bibitem{consensus} Palo Alto AI Research Lab. claude-consensus: A multi-machine consensus protocol for LLM agent fleets. \url{https://github.com/Palo-Alto-AI-Research-Lab/claude-consensus}, 2026. MIT license.
\end{thebibliography}

\end{document}
